### 2016-08-30 README.Rmd
fix readme

```{r env, echo=FALSE}
opts_chunk$set(comment=NA, echo=FALSE)
```

@@

```{r}
auth <- packageDescription("MSnbase")$Author
ctrb <- sub("<lg390@cam.ac.uk> ", "",
            gsub("\t", " ", gsub("\n", " ", auth)))
cat(gsub("  ", " ", ctrb), "\n")
```

>>>>

```{r env, echo=FALSE}
opts_chunk$set(comment=NA)
```

@@

```{r, echo=FALSE}
auth <- packageDescription("MSnbase")$Author
auth <- sub("<lg390@cam.ac.uk> ", "", auth)
auth <- gsub("\n\t", "\n", auth)
auth <- gsub("\t", " ", auth)
cat(auth, "\n")
```
